---
title: "Final"
author: "Jonathan Reimer-Berg"
date: '2022-04-30'
output: pdf_document
---

```{r}
library(ggplot2)
library(socviz)
library(ggthemes)
library(maps)
library(tidyverse)
library(dplyr)
```

```{r}
data <- read.csv("final_bird_data.csv")
USData <- read.csv("USData.csv")
```

```{r}
data <- distinct(data, name,state, .keep_all= TRUE)

bird_data <- data %>%
    group_by(state) %>%
    summarize(total = n()) 

USData$region <- str_to_title(USData$region)
USData$state <- state.abb[match(USData$region, state.name)]

final_data <- left_join(USData, bird_data)
```

```{r}
p0 <- ggplot(data = final_data,
             aes(x = long, y = lat, group = group, fill = total))

p1 <- p0 + geom_polygon(color = "white", size = 0.25) +
    coord_map(projection = "albers", lat0 = 39, lat1 = 45) 

p2 <- p1 + scale_fill_gradientn(colours = c("#ffe657", "tomato", "#ff033e"), na.value = "grey90") +
  labs(title = "Number of birds seen in each state")
                                
p2 + theme_map() + labs(fill = "Total Birds")
```

The above map is a recreation of the My eBird map that is visible for each eBird user summerizing the number
of species seen in each location (there's is clickable, showing data by country, state, and county). All of the colors
and data is therefore a replication of that map, with the data used to create it gotten from eBird. The main stories here are
the two places I have spend the most time, Oregon and Virignia, with several other states also being darker that are good 
for birds (Florida and Colorado). Python was necessary for formatting the data for easy use in r. 

